---
title: "EDA of Armed Conflict"
format: pdf
editor: visual
author: Desmond Chen
---

```{r}
library(here)
library(tidyverse)
finaldata <- read.csv(here("data", "finaldata.csv"), header = TRUE)
names(finaldata)
```
```{r}
finaldata$earthquake[is.na(finaldata$earthquake)] <- 0
finaldata$drought[is.na(finaldata$drought)] <- 0
```

```{r}
finaldata %>%
  dplyr::filter(Country.Name == "Canada")
```
```{r}
summary(finaldata)
```
Maternal mortalities is the outcome with the most missingness of 426, followed by gdp with a missing count of 62. There seems to be a country that was not included in the covariates data, hence we see a missing count of 20 across several covariates.

```{r}
library(ggplot2)
ggplot(data.frame(finaldata$total_best), aes(x = finaldata$total_best)) +
  geom_histogram() +
  scale_y_log10() +
  labs(title = "Histogram of total death with Log Y-axis",
       x = "Death",
       y = "Count (log scale)") +
  theme_minimal()
```
We see a lot outliers at around 55000 death, these could be caused by war happening at certain region.

```{r}
library(ggplot2)
ggplot(data.frame(finaldata$MatMor), aes(x = finaldata$MatMor)) +
  geom_histogram() +
  scale_y_log10() +
  labs(title = "Histogram of maternal mortality with Log Y-axis",
       x = "Death",
       y = "Count (log scale)") +
  theme_minimal()
```
Maternal mortality looks fine, and not any outliers.
```{r}
library(ggplot2)
ggplot(data.frame(finaldata$InfMor), aes(x = finaldata$InfMor)) +
  geom_histogram() +
  scale_y_log10() +
  labs(title = "Histogram of maternal mortality with Log Y-axis",
       x = "Death",
       y = "Count (log scale)") +
  theme_minimal()
```

Infant mortalities looks fine as well.

```{r}
library(ggplot2)
ggplot(data.frame(finaldata$NeoMor), aes(x = finaldata$NeoMor)) +
  geom_histogram() +
  scale_y_log10() +
  labs(title = "Histogram of maternal mortality with Log Y-axis",
       x = "Death",
       y = "Count (log scale)") +
  theme_minimal()
```

```{r}
library(ggplot2)
ggplot(data.frame(finaldata$U5Mor), aes(x = finaldata$U5Mor)) +
  geom_histogram() +
  scale_y_log10() +
  labs(title = "Histogram of maternal mortality with Log Y-axis",
       x = "Death",
       y = "Count (log scale)") +
  theme_minimal()
```

```{r}
cor(finaldata[,c(4:7)], use = "complete.obs")
```
We can see the main outcomes are highly correlated, so we need to be cautious when running them one by one.
