---
title: "Week11"
format: html
editor: visual
---

```{r}
library(here)
df <- read.csv(here("data", "finaldata.csv"), header = TRUE)
df7 <- df[df$year==2017,]
df7 <- df7[!is.na(df7$infmor),]
```

```{r}
library(boot)

getmeddiff <- function(data, indices) {
  sample_data <- data[indices, ]
  group_meds <- tapply(sample_data$infmor, sample_data$armcon, FUN = function(x) median(x,na.rm=TRUE))
  meddiff <- group_meds[2] - group_meds[1]
  return(meddiff)
}

bootout <- boot(df7, statistic = getmeddiff, strata = df7$armcon, R = 1000)
bootout
```

## Infant Mortality

```{r}
boot.ci(boot.out = bootout, conf = 0.95, type = c("basic", "perc", "bca"))
```
Upper bound and lower bound in Basic is higher in Basic, while percentile is on the lower end, finally BCa is right in the middle.


```{r}
getmeddiff <- function(data, indices) {
  sample_data <- data[indices, ]
  group_meds <- tapply(sample_data$neomor, sample_data$armcon, FUN = function(x) median(x,na.rm=TRUE))
  meddiff <- group_meds[2] - group_meds[1]
  return(meddiff)
}

bootout <- boot(df7, statistic = getmeddiff, strata = df7$armcon, R = 1000)
bootout
```

## Neonatal Mortality

```{r}
boot.ci(boot.out = bootout, conf = 0.95, type = c("basic", "perc", "bca"))
```
Upper bound and lower bound in Basic is higher in Basic, while percentile and BCa was lower and consistent.

## Under 5 Mortality

```{r}
getmeddiff <- function(data, indices) {
  sample_data <- data[indices, ]
  group_meds <- tapply(sample_data$un5mor, sample_data$armcon, FUN = function(x) median(x,na.rm=TRUE))
  meddiff <- group_meds[2] - group_meds[1]
  return(meddiff)
}

bootout <- boot(df7, statistic = getmeddiff, strata = df7$armcon, R = 1000)
bootout
```

```{r}
boot.ci(boot.out = bootout, conf = 0.95, type = c("basic", "perc", "bca"))
```
Upper bound and lower bound in Basic is higher in Basic, while percentile is on the lower end, finally BCa is right in the middle.