---
title: "R Notebook"
output: html_notebook
---


```{r}
library(here)
library(tidyverse)
here()
rdf <- read.csv(here("original","maternalmortality.csv"),header = T)
```

a. Use the select() function in the dplyr package (which is one of the packages in
the tidyverse bundle) to subset the data to have only the variables Country.Name,
X2000 – X2019.
```{r}
sdf <- select(rdf,c(Country.Name,X2000:X2019))
```

b. The data set is currently in a wide format. Use the pivot_longer() function to
convert the data set into a long format. So that the first and last 20 rows of the
resulting data set look like this. Hint: You need to select the columns X2000 to
X2019, remove the prefix X from them, change the name of the variable to
Year, change the values to MatMor. Finally, make sure the year variable is stored
as numeric.
```{r}
names(sdf) <- c("Country.Name",2000:2019)
ldf <- pivot_longer(sdf, cols = c(2:21),names_to = "year",values_to = "MatMor")
```
 
```{r}
write_csv(ldf,here("data","MatMor.csv"))
```

```{r}
prepdf <- function(x,y){
  rdf <- read.csv(here("original",x),header = T)
  sdf <- select(rdf,c(Country.Name,X2000:X2019))
  names(sdf) <- c("Country.Name",2000:2019)
  return(pivot_longer(sdf, cols = c(2:21),names_to = "year",values_to = y))
}
```

```{r}
i <- prepdf("infantmortality.csv","InfMor")
n <- prepdf("neonatalmortality.csv","NeoMor")
u <- prepdf("under5mortality.csv","U5Mor")
m <- prepdf("maternalmortality.csv","MatMor")
```

```{r}
sum(i$Country.Name==n$Country.Name)
sum(i$year==n$year)
sum(u$Country.Name==n$Country.Name)
sum(u$year==n$year)
sum(u$Country.Name==m$Country.Name)
sum(u$year==m$year)
```
```{r}
worldbank <- cbind(m,InfMor=i$InfMor,NeoMor=n$NeoMor,U5Mor=u$U5Mor)
```

```{r}
library(countrycode)
worldbank$ISO <- countrycode(worldbank$Country.Name,origin = "country.name",destination = "iso3c")
```

